Model Samples Processing

### 2020-01-24 stats/model_sample_processing.Rmd
add mode run with random effects

model <- bind_rows(
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-10_burn0_lag0_chain1.csv")%>%mutate(chain = 1)
)

@@

saveRDS(model_pred, "../saves/model_pred.rds")

@@

saveRDS(item_params, "../saves/item_params.rds")

@@

saveRDS(global_params, "../saves/global_params.rds")

@@

saveRDS(item_sigma, "../saves/item_sigma.rds")

@@

saveRDS(subject_sigma, "../saves/subject_sigma.rds")
```

>>>>

model <- bind_rows(
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain1.csv")%>%mutate(chain = 1),
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain2.csv")%>%mutate(chain = 2)
)

@@

saveRDS(model_pred, "../saves/model_pred_re.rds")

@@

saveRDS(item_params, "../saves/item_params_re.rds")

@@

saveRDS(global_params, "../saves/global_params_re.rds")

@@

saveRDS(item_sigma, "../saves/item_sigma_re.rds")

@@

saveRDS(subject_sigma, "../saves/subject_sigma_re.rds")
```
